DCM_investigation

### 2020-11-12 article_figures_ARTHUR_CAPET.Rmd
light update 2

                            ISOalow       = try_default(approx(x=depth, y=light_absolute, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            ISOa90B       = try_default(approx(x=depth, y=light_absolute, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            ISOa90T       = try_default(approx(x=depth, y=light_absolute, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            ISOaMLD       = try_default(approx(x=depth, y=light_absolute, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
                            ISOaMAX       = try_default(approx(x=depth, y=light_absolute, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            ISOaDEMI      = try_default(approx(x=depth, y=light_absolute, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
                            ISOa_iso1     = try_default(approx(x=depth, y=light_absolute, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)

@@

#relative light
#tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))

@@

relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab('% of Incoming PAR') +  scale_y_continuous(trans = 'log10') +
  scale_color_manual(aesthetics = c("colour", "fill"),
                         values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                   TeX('$\\ISO_{low}$'),
                                   TeX('$\\ISO_{50,bottom}$'),
                                   TeX('$\\ISO_{50,top}$'),
                                   TeX('$\\ISO_{1%}$')))

@@

absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
#              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  scale_y_continuous(trans = 'log10') +
  ylab(TeX('$\\mu molQuanta\\,m^{-2}\\,s^{-1}]$')) +
  scale_color_manual(aesthetics = c("colour", "fill"),
                     values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$')))

>>>>

                            ISOalow       = try_default(approx(x=depth, y=absolute_light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            ISOa90B       = try_default(approx(x=depth, y=absolute_light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            ISOa90T       = try_default(approx(x=depth, y=absolute_light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            ISOaMLD       = try_default(approx(x=depth, y=absolute_light, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
                            ISOaMAX       = try_default(approx(x=depth, y=absolute_light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            ISOaDEMI      = try_default(approx(x=depth, y=absolute_light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
                            ISOa_iso1     = try_default(approx(x=depth, y=absolute_light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)

@@

tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))

@@

relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
                              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab('% of Incoming PAR') +  scale_y_continuous(trans = 'log10') +
  scale_color_manual(aesthetics = c("colour", "fill"),
                         values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                   TeX('$\\ISO_{low}$'),
                                   TeX('$\\ISO_{50,bottom}$'),
                                   TeX('$\\ISO_{50,top}$'),
                                   TeX('$\\ISO_{1%}$')))

@@

absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  scale_y_continuous(trans = 'log10') +
  ylab(TeX('$\\mu molQuanta\\,m^{-2}\\,s^{-1}]$')) +
  scale_color_manual(aesthetics = c("colour", "fill"),
                     values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$')))
